Traffic aware Resource Allocation for \acs{MIMO}-\acs{OFDM} systems

### 2014-09-15 Report/kkt_mse_approach.tex
Final version before revision to all

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 \nonumber \\
&\hspace{0.5cm}& \qquad {} \qquad {} + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & - \log(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \geq t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.

By forming the Lagrangian of \eqref{kkt-mse-1} with the corresponding dual variables as shown in \eqref{kkt-mse-1}, we can obtain the \ac{KKT} expressions by differentiating with respect to the variables present in the problem as detailed in Appendix \ref{a-1}. Upon solving the \ac{KKT} expressions, the iterative solution \me{\forall k \in \mc{U}}, \me{\forall n \in \set{1,\ldots,N}} and \me{\forall l \in \set{1,\ldots,L}} is given by
\begin{IEEEeqnarray}{rCl} \label{kkt-mse-4}
\mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
\sigma_{l,k,n}^{(i)} &=& \max{\left (0, \frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right )}  \IEEEyessubnumber \label{kkt-mse-4.2} \\
\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \dfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}
\end{IEEEeqnarray}
Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other. In this problem, we fix the dual variable \me{\alpha^{(i)}} to a fixed value as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}. It can be seen that, when the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing the dual variable \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}}, which in turn reduce the transmit precoder weights in \eqref{kkt-mse-4.3}. This reduction in the precoder weights forces the allocated rate of the user \me{k} to reduce from the previous iteration as \me{t_k^{(i)} < t_k^{(i-1)}}.

@@

In order to perform the distributed approach, we can consider the method proposed in \cite{komulainen2013effective}, where the users evaluate the \ac{MSE}, and the dual variable \me{\alpha_{l,k,n}} using the transmission made by all \acp{BS} using the updated transmit precoders \me{\mvec{m}{l,k,n}^{(i-1)}}. Once the dual variables are evaluated, the users will notify the dual variables and the receive beamformers to the \acp{BS} using uplink precoded pilots, where the uplink precoder is given by \me{\mvec{\tilde{w}}{l,k,n}^{(i-1)} = \sqrt{\alpha_{l,k,n}^{(i-1)}}\mvec{w}{l,k,n}^{\ast(i-1)}}. Upon receiving the uplink precoded pilots at the \ac{BS} \me{b}, the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i-1)}} can be measured and used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} represents the conjugate of \me{\mbf{x}}. The algorithmic representation of the distributed \ac{MSE}-\ac{KKT} scheme is shown in the Algorithm. \ref{algo-4}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=1} and the receive beamformers \me{\mbf{w}^{(0)}_{l,k,n}} randomly}
 \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly and the dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}}
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 set the maximum iteration counter \me{I_{\max},J_{\max}} to a valid number. \;
 initialize \me{j = 0}. \;
 \Repeat{until convergence or \me{j \geq J_{\max}}}{
 initialize \me{i = 0}. \;
 \Repeat{until convergence or \me{i \geq I_{\max}}}{
	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, where \me{\delta_b} is identified by the bisection method satisfying \eqref{kkt-mse-1.4}. \;
    update \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at the receivers using the transmit precoders \me{\mvec{M}{k,n}^{(i)}} from all \acp{BS}. \;
    perform precoded uplink pilot transmission from all users with the precoder \me{\mvec{\tilde{w}}{l,k,n}^{(j)}}. \;
    \me{i = i + 1} \;
  }
 evaluate the receive beamforming vector \me{\mvec{W}{k,n}^{(j+1)}} using \eqref{kkt-mse-4.6}. \;
 inform \acp{BS} using uplink precoded pilot transmission from all users with the precoder \me{\mvec{\tilde{w}}{l,k,n}^{(j+1)}}. \;
 \me{j = j + 1}. \;
 }
 \caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
 \label{algo-4}
\end{algorithm}

>>>>

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.

By forming the Lagrangian of \eqref{kkt-mse-1} with the corresponding dual variables as shown in \eqref{kkt-mse-1}, we can obtain the \ac{KKT} expressions by differentiating with respect to the variables present in the problem as detailed in Appendix \ref{a-1}. Upon solving the \ac{KKT} expressions, the iterative solution \me{\forall k \in \mc{U}}, \me{\forall n \in \set{1,\ldots,N}} and \me{\forall l \in \set{1,\ldots,L}} is given by
\begin{IEEEeqnarray}{rCl} \label{kkt-mse-4}
\mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
\sigma_{l,k,n}^{(i)} &=& \max{\left \lbrace 0, \frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right \rbrace }  \IEEEyessubnumber \label{kkt-mse-4.2} \\
\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \dfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}
\end{IEEEeqnarray}
Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other. In this problem, we fix the dual variable \me{\alpha^{(i)}} to a fixed value as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}. It can be seen that, when the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing the dual variable \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}}, which in turn reduce the transmit precoder weights in \eqref{kkt-mse-4.3}. This reduction in the precoder weights forces the allocated rate of the user \me{k} to reduce from the previous iteration as \me{t_k^{(i)} < t_k^{(i-1)}}.

@@

In order to perform the distributed approach, we can consider the method proposed in \cite{komulainen2013effective}, where the users evaluate the \ac{MSE}, and the dual variable \me{\alpha_{l,k,n}} using the transmission made by all \acp{BS} using the updated transmit precoders \me{\mvec{m}{l,k,n}^{(i-1)}}. Once the dual variables are evaluated, the users will notify the dual variables and the receive beamformers to the \acp{BS} using uplink precoded pilots, where the uplink precoder is given by \me{\mvec{\tilde{w}}{l,k,n}^{(i-1)} = \sqrt{\alpha_{l,k,n}^{(i-1)}}\mvec{w}{l,k,n}^{\ast(i-1)}}. Upon receiving the uplink precoded pilots at the \ac{BS} \me{b}, the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i-1)}} can be measured and used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} represents the conjugate of \me{\mbf{x}}. The algorithmic representation of the distributed \ac{MSE}-\ac{KKT} scheme is shown in the Algorithm. \ref{algo-4}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=1} and the receive beamformers \me{\mbf{w}^{(0)}_{l,k,n}} randomly}
 \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly and the dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}}
 \ForEach{\ac{BS} \me{b \in \mc{B}}}{
 set the maximum iteration counter \me{I_{\max},J_{\max}} to a valid number. \;
 initialize \me{i = 0}. \;
 \Repeat{until convergence or \me{i \geq I_{\max}}}{
 initialize \me{j = 0}. \;
 \Repeat{until convergence or \me{j \geq J_{\max}}}{
	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, where \me{\delta_b} is identified by the bisection method satisfying \eqref{kkt-mse-1.4}. \;
    update \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at the receivers using the transmit precoders \me{\mvec{M}{k,n}^{(i)}} from all \acp{BS}. \;
    perform precoded uplink pilot transmission from all users with the precoder \me{\mvec{\tilde{w}}{l,k,n}^{(j)}}. \;
  \me{j = j + 1}. \;
  }
 evaluate the receive beamforming vector \me{\mvec{W}{k,n}^{(j+1)}} using \eqref{kkt-mse-4.6}. \;
 inform \acp{BS} using uplink precoded pilot transmission from all users with the precoder \me{\mvec{\tilde{w}}{l,k,n}^{(j+1)}}. \;
 \me{i = i + 1} \;
 }
 }
 \caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
 \label{algo-4}
\end{algorithm}

### 2014-09-15 Report/simulation_results.tex
Final version before revision to all

In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with lower path loss. Fig. \ref{fig-1} shows the performance of the centralized schemes for a single receive antenna system. It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
\begin{figure*}
\centering
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-1-3}
\label{fig-1}}
\hfill
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,3,9,4,2\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-2-2}
\label{fig-2}}
\caption{Number of backlogged packets at the \ac{SCA} update points}
\label{fig-a}
\end{figure*}

In the sub-channel wise allocations, where the total transmit power is shared equally among the sub-channels, the precoders are designed for each sub-channels independently. In this approach, the precoders are coupled via the number of queued bits which are updated using \eqref{eqn-weight} before designing the precoders for the sub-channels. At each \ac{SCA} points, the number of queued bits are reduced significantly with the introduction of a new sub-channel since the algorithm starts with a random initial point before it converges to an optimal\footnote{due to the nonconvex nature of the original problem} precoders. The total number of backlogged bits at each \ac{SCA} update instant are plotted in Fig. \ref{fig-1} for the discussed centralized schemes and the convergence point are marked with the data tips. Fig. \ref{fig-2} compares the performance of the centralized algorithms for the \me{N_R = 2} receive antennas. In all the schemes, the receive beamformers are updated at the \ac{SCA} update points instead of updating after the \ac{SCA} convergence as in Algorithm. \ref{algo-1}. Since the receiver minimizes the objective for the fixed transmit precoders, the convergence is monotonic as can be seen from the figures.
\begin{table}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\begin{tabular}{|c|*{8}{c}|c|}
\hline
\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
\hline
\me{1} & 15.00 & 3.95 & 5.26 & 8.95 & 7.03 & 11.90 & 12.00 & 9.73 & 25.15 \\
\me{2} & 11.23 & 3.93 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.90 & 27.77 \\
\me{\infty} & 11.41 & 4.41 & 10.41 & 10.41 & 10.41 & 8.41 &  8.41 &  6.41 & 28.68 \\
\hline
\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\
\cline{1-9}
\end{tabular}
\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
\label{tbl-3}
\end{table}
%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{tbl-2}
%\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
%\label{tbl-3}
%\end{figure}

>>>>

In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with lowest path loss component. Fig. \ref{fig-1} shows the performance of the centralized schemes for a single receive antenna system. It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
\begin{figure*}
\centering
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-1-3}
\label{fig-1}}
\hfill
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-2-4}
\label{fig-2}}
\caption{Number of backlogged packets at the \ac{SCA} update points}
\label{fig-a}
\end{figure*}

Fig. \ref{fig-a} compares the performance of the centralized algorithms with the total number of residual bits remaining in the system after the current transmission slot. The reduction in the number of queued packets after each \ac{SCA} updates are plotted in the figures. It can be seen from Fig. \ref{fig-a}, the \ac{Q-WSRM} algorithm is not optimal due to the problem of over allocation when the number of queued packets are small. In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over allocation problem. It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}. It can be seen that all the algorithms are Pareto-optimal and provides different performance based on the weights used to find a point in the rate region.

In the scenario defined by Fig. \ref{fig-a}, \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the rate maximization algorithm. The performance degradation can be attributed to the fact that the \ac{Q-WSRME} algorithm favors the users with the large number of backlogged packets as compared to the users with better channel conditions. Fig. \ref{fig-2} compares the algorithms for \me{N_R = 2} receive antenna case. In all figures, the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} in the Algorithm \ref{algo-1}. It is also noted that the performance degradation by performing the group update is very minimal. Since the receiver minimizes the objective for the fixed transmit precoders, the convergence is monotonic as can be seen from the figures.
\begin{table}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\begin{tabular}{|c|*{8}{c}|c|}
\hline
\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
\hline
\me{1} & 15.00 & 3.95 & 5.26 & 8.95 & 7.03 & 11.90 & 12.00 & 9.73 & 25.15 \\
\me{2} & 11.23 & 3.93 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.90 & 27.77 \\
\me{\infty} & 11.41 & 4.41 & 10.41 & 10.41 & 10.41 & 8.41 &  8.41 &  6.41 & 28.68 \\
\hline
\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\
\cline{1-9}
\end{tabular}
\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
\label{tbl-3}
\end{table}
%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{tbl-2}
%\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
%\label{tbl-3}
%\end{figure}
